Scoring Patients

### 2017-05-23 Patient Report.Rmd
Starting to firm up analysis

---
title: "Scoring Patients"
author: "Sarah Killcoyne"
date: "15 November 2016"
output:
  html_document: 
    toc: yes
  word_document: default
---

```{r setup, include=FALSE}
library(ggplot2)
library(GGally)
library(plyr)
#library(xlsx)
library(dplyr)
library(pander)
#library(Hmisc)
library(ggdendro)
library(reshape2)
library(GenomicRanges)
library(gridExtra)
library(tibble)

@@

```{r, hmm, echo=F, message=F, warning=F, fig.height=40, fig.width=10}
ccgenes = read.table('~/Data/CosmicCensusGenes.tsv', sep='\t', header=T, stringsAsFactors=F)

@@

m = melt(gene.p[,c(1:4)], id.vars=c('Gene.Symbols', 'CN'))
m$Gene.Symbols = factor(m$Gene.Symbols, levels=unique(m$Gene.Symbols[c(nrow(m):1)]) ) # order
m$CN = factor(m$CN)

ggplot(m, aes(y=Gene.Symbols, x=variable)) + 
  geom_tile(aes(fill=value), color='white') + 
  scale_fill_gradient('n patients',low='white',high='red') + labs(x="",y='CGC Genes') +
  geom_point(data=m[m$CN == 'gain' & m$value > 0,], aes(y=Gene.Symbols, x=variable), size=2, shape=24, fill='red', color='red') +
  geom_point(data=m[m$CN == 'loss' & m$value > 0,], aes(y=Gene.Symbols, x=variable), color='green4', size=2, shape=25, fill='green4')

gc = ddply(gene.cnt, .(Gene.Symbols), summarise, Progressors=sum(Progressors), Non.Progressors=sum(Non.Progressors))
gc = arrange(subset(gc, Progressors >= Non.Progressors), -Progressors)
gc = gc[1:60,]
m = melt(gc, id.vars=c('Gene.Symbols'))
#m$value = as.factor(m$value)
m$Gene.Symbols = factor(m$Gene.Symbols, levels=unique(m$Gene.Symbols[c(nrow(m):1)]) ) # order
ggplot(m, aes(y=Gene.Symbols, x=variable)) + 
  geom_tile(aes(fill=value), color='white') + 
  scale_fill_gradient('n patients',low='white',high='red') + labs(x="",y='CGC Genes') + ggtitle("Top 50 genes only")

@@

>>>>

---
title: "Scoring Patients"
author: "Sarah Killcoyne"
date: "23 May 2017"
output:
  html_document: 
    toc: yes
  word_document: default
---

```{r setup, include=FALSE}
library(ggplot2)
library(GGally)
library(plyr)
library(RColorBrewer)
library(dplyr)
library(pander)
library(ggdendro)
library(reshape2)
library(GenomicRanges)
library(gridExtra)
library(tibble)

@@

```{r, hmm, echo=F, message=F, warning=F, fig.height=100, fig.width=10}
ccgenes = read.table('~/Data/CosmicCensusGenes.tsv', sep='\t', header=T, stringsAsFactors=F)

@@

gene.p = gene.p[,(1:4)]
m = melt(gene.p, id.vars=c('Gene.Symbols', 'CN'))
m = transform(m, Gene.Symbols = reorder(Gene.Symbols, value))

#m$Gene.Symbols = factor(m$Gene.Symbols, levels=unique(m$Gene.Symbols[c(nrow(m):1)]) ) # order
m$CN = factor(m$CN)

m$brks <- cut(m$value, include.lowest=T, right=F,
                   breaks=c(0, 1, 3, 5, 8, 10),
                   labels=c('0','1-3', '4-5', '6-8','9-10'))
m = transform(m, Gene.Symbols = reorder(Gene.Symbols, value))

myP = c('white',brewer.pal(n = length(levels(m$brks)), name = "Reds"))

ggplot(m, aes(y=Gene.Symbols, x=variable)) + 
  geom_tile(aes(fill=brks), color='white') + scale_fill_manual( values = myP, "Patient Counts") +
  geom_point(data=subset(m, value > 0), aes(y=Gene.Symbols, x=variable, shape=CN, color=CN), size=3 ) +
  scale_color_manual("CN", values=c("blue", "yellow")) + scale_shape_manual(values=c(17,20)) +
  labs(title="All available COSMIC genes mapped", x='', y='')

@@

Just the top 50 genes by the number of patients that share variants in these regions.

```{r echo=F, warning=F, message=F, fig.height=12, fig.width=8}

m = melt(gene.p[1:50,], id.vars=c('Gene.Symbols', 'CN'))
m = transform(m, Gene.Symbols = reorder(Gene.Symbols, value))

m$brks <- cut(m$value, include.lowest=T, right=F,
                   breaks=c(0, 1, 3, 5, 8, 10),
                   labels=c('0','1-3', '4-5', '6-8','9-10'))

ggplot(m, aes(y=Gene.Symbols, x=variable)) + 
  geom_tile(aes(fill=brks), color='white') + scale_fill_manual( values = myP, "Patient Counts") +
  geom_point(data=subset(m, value > 0), aes(y=Gene.Symbols, x=variable, shape=CN, color=CN), size=3 ) +
  scale_color_manual("CN", values=c("blue", "yellow")) + scale_shape_manual(values=c(17,20)) +
  labs(title="Top 50 genes by number of patients", x='', y='')
```
